Numerical Stability of Detonations in White Dwarf Simulations

### 2019-02-23 papers/ignition/paper.tex
Add caveat about the test being artificial

\added{We also tested a similar configuration made of pure carbon/oxygen material (equal fraction by mass).
This is closer to the configuration used in the $0.64\ \msolar$ WD collision simulations that previous
papers have focused on. However, for the setup described above, pure carbon/oxygen conditions do not
detonate at all. This is not particularly surprising, since the 1D setup is a very imperfect representation
of the real multi-dimensional case, and is missing multi-dimensional hydrodynamics that could substantially
alter the dynamical evolution. So the small amount of helium we added above ensured that the setup ignited.
(Of course, there will likely be a small amount of helium present in C/O white dwarfs as a remnant of the prior
stellar evolution.) However, we can prompt the C/O setup to ignite by starting the initial temperature
at $10^9$ K instead of $10^7$ K. This loosely mimics the effect from the first test, where helium burning
drives the temperature to the conditions necessary to begin substantial burning in C/O material. But since
no helium is present in this case, it allows us to test whether it is easier to obtain convergence for pure
C/O burning. The results for this case are shown in \autoref{fig:self-heat-distance-co}. In this case, the
ignition is central at all resolutions, but the simulation is still clearly unconverged at resolutions worse
than 100 m.}

>>>>

\added{We also tested a similar configuration made of pure carbon/oxygen material (equal fraction by mass).
This is closer to the configuration used in the $0.64\ \msolar$ WD collision simulations that previous
papers have focused on. However, for the setup described above, pure carbon/oxygen conditions do not
detonate at all. This is not particularly surprising, since the 1D setup is a very imperfect representation
of the real multi-dimensional case, and is missing multi-dimensional hydrodynamics that could substantially
alter the dynamical evolution. So the small amount of helium we added above ensured that the setup ignited.
(Of course, there will likely be a small amount of helium present in C/O white dwarfs as a remnant of the prior
stellar evolution.) However, we can prompt the C/O setup to ignite by starting the initial temperature
at $10^9$ K instead of $10^7$ K. This loosely mimics the effect from the first test, where helium burning
drives the temperature to the conditions necessary to begin substantial burning in C/O material. But since
no helium is present in this case, it allows us to test whether it is easier to obtain convergence for pure
C/O burning, even though the test itself is artificial. The results for this case are shown in
\autoref{fig:self-heat-distance-co}. In this case, the ignition is central at all resolutions, but the
simulation is still clearly unconverged at resolutions worse than 100 m, as the ignition becomes significantly
delayed at high resolution.}
